---
title: "R Notebook"
output: html_notebook
---
```{r}
ptype <- "eps"
```

Save figures

Make map of RBI and of CV for all sites

Figure 1. Map of sites colored by KGC map with table
From RMD: cfs general stats
```{r}
ggsave("Figure1_pts_map.eps", site_table, 
       device = ptype, path = "OutputPlots/",
       width = 10,
       height = 10,
       units = "in")
```

Figure 2. Example Timeseries
From RMD: example_discharge
```{r}
ggsave("Figure2_ex_ts.eps", EX_ts_flashy, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```

Figure 3. Violin plots of RB paper sizes
CONUS points
From RMD: cdfs general stats
```{r}
ggsave("Figure3_rb_violins.eps", rbviolins, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")

ggsave("Figure_CONUS_pts.eps", rbviolins, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```

Figure 4. RB paper size boxplots with KGC map
From RMD: cdfs general stats
```{r}
ggsave("Figure4_map_rbboxplots.eps", KGmap_RBboxplots, 
       device = ptype, path = "OutputPlots/",
       width = 7,
       height = 8,
       units = "in")
```
Figure 4-2. Size v. RBI
```{r}
ggsave("Figure4_2_RBI_Size_Scatter.eps",sizeRBI, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 5,
       units = "in")
```


Figure 5. Size v RBI point clouds with linear fits and map
From RMD: cdfs general stats
```{r}
ggsave("Figure5_map_points.eps", KGmap_points, 
       device = ptype, path = "OutputPlots/",
       width = 7,
       height = 8,
       units = "in")
```

Figure 6. Slope v. RBI
from RMD: cdfs general stats
```{r}
ggsave("Figure6_slope_rbi.eps", SLOPEkgc, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```

Figure 7. Developed land v. RBI
from RMD: cdfs general stats
```{r}
ggsave("Figure7_devland_rbi.eps", devlandRBI, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```

Figure 8. RF predictors v importance for all sites colored by "Type"
in: random forest
```{r}
#some variables are the same in this and the per KGC RF, so be sure to re-run
ggsave("Figure8_RF_import_CONUS.eps", RF_import_ALL, 
       device = ptype, path = "OutputPlots/",
       width = 7,
       height = 8,
       units = "in")
```

Figure 9. RF predictor categories for KGCs, include map as top panel
in: random forest PER KGC
```{r}
ggsave("Figure9_RFsums_perKGC.eps", RFsummary_KGCs, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```

Figure 10. Points on a map colored by RBI
```{r}
ggsave("Figure10_RBI_map.eps", RBImap, 
       device = ptype, path = "OutputPlots/",
       width = 10,
       height = 6,
       units = "in")
```

Figure 11. Points on a map colored by log RBI
```{r}
ggsave("Figure11_logRBI_map.eps", RBImaplog, 
       device = ptype, path = "OutputPlots/",
       width = 10,
       height = 6,
       units = "in")
```

Figure 12. Points on a map colored by RBI CV
```{r}
ggsave("Figure12_RBI_cv_map.eps", RBImapCV, 
       device = ptype, path = "OutputPlots/",
       width = 10,
       height = 6,
       units = "in")
```

Figure 13. Points on a map colored by ref non ref
```{r}
ggsave("Figure13_ref_nonref_map.eps", ReferenceSiteMap, 
       device = ptype, path = "OutputPlots/",
       width = 10,
       height = 6,
       units = "in")
```

Figure 14. cv of RBI vs drainage area log scale
```{r}
ggsave("Figure14_RBIvsVSdrainage.eps", RBIcvVSdrainage, 
       device = ptype, path = "OutputPlots/",
       width = 6,
       height = 4,
       units = "in")
```